Measuring Directionality in Double Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-07-22 Direction_v6.tex
Version 6 of draft. Rounded Q-values for 116Cd. --Christoph

Most of the high Q-value candidates
have been considered as a dopant for a liquid scintillator:
$^{150}$Nd(Q=3.367~MeV)\cite{minfang,nd1}, $^{96}$Zr(Q=3.350~MeV)\cite{zr1},
$^{100}$Mo(Q=3.034~MeV)\cite{mo1}, $^{82}$Se(Q=3.350~MeV)\cite{qdot},
$^{116}$Cd(Q=2.802~MeV)\cite{qdot, cd1}, $^{130}$Te(Q=2.533~MeV)\cite{qdot, biller},
$^{136}$Xe(Q=2.479~MeV)\cite{KZ0nu} and $^{124}$Sn(Q=2.29~MeV)\cite{sn1}.
Xenon gas readily dissolves into liquid scintillator. For the other isotopes,
a suitable organometallic compound needs to be found that produces a stable
scintillator with a long attenuation length in the wavelength region of
interest. As an alternative to single-atom-doping, recently nanocrystals 
formed by candidate isotopes have been explored as a dopant\cite{qdot,qdot2}.

@@

\begin{figure}
        \begin{center}
        \includegraphics[scale=0.4]{graphs/geometry_plot_labels.pdf}
        \caption[]{The detector geometry and coordinate system.
        The radial rays (green lines) are photons emitted by two back-to-back electrons with 1.41~MeV each
        (equally divided energy of $^{116}$Cd~$0\nu\beta\beta$ decay). The electrons originate at
        the center of the sphere with initial directions along the x
        and -x-axis. Only Cherenkov photons are drawn to illustrate the
        directionality of the event. \label{detector_view}}
        \end{center}
\end{figure}

>>>>

Most of the high Q-value candidates
have been considered as a dopant for a liquid scintillator:
$^{150}$Nd(Q=3.367~MeV)\cite{minfang,nd1}, $^{96}$Zr(Q=3.350~MeV)\cite{zr1},
$^{100}$Mo(Q=3.034~MeV)\cite{mo1}, $^{82}$Se(Q=3.350~MeV)\cite{qdot},
$^{116}$Cd(Q=2.81~MeV)\cite{qdot, cd1}, $^{130}$Te(Q=2.533~MeV)\cite{qdot, biller},
$^{136}$Xe(Q=2.479~MeV)\cite{KZ0nu} and $^{124}$Sn(Q=2.29~MeV)\cite{sn1}.
Xenon gas readily dissolves into liquid scintillator. For the other isotopes,
a suitable organometallic compound needs to be found that produces a stable
scintillator with a long attenuation length in the wavelength region of
interest. As an alternative to single-atom-doping, recently nanocrystals 
formed by candidate isotopes have been explored as a dopant\cite{qdot,qdot2}.

@@

\begin{figure}
        \begin{center}
        \includegraphics[scale=0.4]{graphs/geometry_plot_labels.pdf}
        \caption[]{The detector geometry and coordinate system.
        The radial rays (green lines) are photons emitted by two back-to-back electrons with 1.4~MeV each
        (equally divided energy of $^{116}$Cd~$0\nu\beta\beta$ decay). The electrons originate at
        the center of the sphere with initial directions along the x
        and -x-axis. Only Cherenkov photons are drawn to illustrate the
        directionality of the event. \label{detector_view}}
        \end{center}
\end{figure}
